Forcing for Isabelle

### 2018-02-12 blueprint.tex
typos

\section{Forcing notions}
We will need the following concepts:
\begin{itemize}
\item Forcing poset or \emph{notion}: a triple $\lb \PP, \1, \leq\rb$ where $\leq$ is a
  partial (pre)order on $\PP$ with (a) top element $\1$.
\item Compatible elements. Antichain in $\PP$. 
\item Dense subset $D\sbq\PP$ of a forcing poset.
\item Filter $G\sbq\PP$ in a poset.
\item $\calD$-generic filter for $\PP$, where $\calD$ is a family of
  dense subsets of $\PP$.
\end{itemize}

@@

This is different from what would $M$ see from ``within.'' In
particular, the universal quantifier should range only over elements
of $M$:
\[
\phi^M\defi\forall p\in M (p\in \PP \limp \lb p,p\rb \in R).
\]
In Isabelle/ZF, we will move to a more general setting, by allowing
that $M$ is a class.
\begin{verbatim}
definition  
  reflexivity_rel :: "[i⇒o,i,i] ⇒ o" where
  "reflexivity_rel(M,P,r) == ∀p[M].  p∈P ⟶ <p,p>∈r"
\end{verbatim}
(Notice: There must be no spaces between \verb|[M]| and the following
period.) This is the relativized version of
\verb|reflexivity_abs|.

>>>>

\section{Forcing notions}
We will need the following concepts:
\begin{itemize}
\item Forcing poset or \emph{notion}: a triple $\lb \PP, \1, \leq\rb$ where $\leq$ is a
  partial (pre)order on $\PP$ with (a distinguished) top element $\1$.
\item Compatible elements. Antichain in $\PP$. 
\item Dense subset $D\sbq\PP$ of a forcing poset.
\item Filter $G\sbq\PP$ in a poset.
\item $\calD$-generic filter for $\PP$, where $\calD$ is a family of
  dense subsets of $\PP$.
\end{itemize}

@@

This is different from what would $M$ see from ``within.'' In
particular, the universal quantifier should range only over elements
of $M$:
\[
\phi^M\defi\forall p\in M (p\in \PP \limp \lb p,p\rb \in R).
\]
In Isabelle/ZF, we will move to a more general setting, by allowing
 $M$ to be a class.
\begin{verbatim}
definition  
  reflexivity_rel :: "[i⇒o,i,i] ⇒ o" where
  "reflexivity_rel(M,P,r) == ∀p[M].  p∈P ⟶ <p,p>∈r"
\end{verbatim}
(Notice: There must be no spaces between \verb|[M]| and the following
period.) This is the relativized version of
\verb|reflexivity_abs|.
